### 2024-06-19 analysis/analysis.qmd
add scripts for analyzing studies

Initial work to build the data parser from the bibTeX files.

@@

```{r}
# preprocessing step for list fields in bibtex files:
source('stripLFFromList.R') # helper function
stripLFFromList(fn = "../studies/test_orig.bib")
library(bib2df) # this parser seems to be give a lot warnings/errors with this data
#anno <- bib2df("../studies/metaMER_library_extraction_first_pass.bib")
anno <- bib2df("../studies/test_orig_strip.bib")
anno
anno<-data.frame(anno)
#anno$MODEL_RATE_EMOTION_VALUES
x <- eval(parse(text = anno$MODEL_RATE_EMOTION_VALUES))
x
anno$MODEL_LIST<-list(x)
anno$MODEL_LIST

length(anno$MODEL_LIST[[1]])

# select two regression studies: grekow2021mu and chen2017co
#anno_ex <- dplyr::filter(anno,BIBTEXKEY=='grekow2021mu'|BIBTEXKEY=='chen2017co')
```

Use paradigm field to process regression and classification studies separately.

We need to identify the core values:
- correlation (obtained from $R^2$)
- n (we use STIMULUS_N rather than participant n)

## Convert / Extract fields

```{r}
# create parser that gets the R2 measures out of the nested data

@@

@@

### Valence

```{r}
# eval: false
library(dmetar)
library(tidyverse)
library(meta)

>>>>

This assumes that the data has been parsed from the BibTeX files into table and exported as CSV file.

@@

- Update 2024-06-19
- TODO: find better way to read in functions

```{r}
require(here)
source(here::here('R/build-df.R'))
source(here::here('R/format-study-results.R'))
source(here::here('R/parse-model-output.R'))
```

```{r}
# get metaMER df:

meta_df <- get_metaMER_df(path_2_studies = here::here('studies'))

# get included studies

included_studies <- meta_df[which(
  !stringr::str_detect(meta_df$final_notes, '!EXCL!')),] |> 
  dplyr::tibble()

@@

```{r}
# get studies re-coded (currently identifiable by presence of bind_field.)
recoded_studies <- included_studies[which(stringr::str_detect(
  included_studies$model_rate_emotion_values,
                                     'bind_field')),]

```{r}
metaMER_results <- do.call(rbind,
lapply(recoded_studies$model_rate_emotion_values, 
       parse_model_output)
)

metaMER_results |> dplyr::tibble()

```{r}
#| eval: false
d <- read.csv('data/meta-analysis_data.csv')
```

We need to identify the core metrics:

- _correlation coefficient_ (obtained from $R^2$) for regression studies.

- _Matthew's correlation coefficient_ for classification studies.

- n (we use STIMULUS_N rather than participant n)

- Subsetting base on model and music qualities

@@

#### Valence

```{r}
#| warning: false
#| eval: false
library(dmetar)
library(tidyverse)
library(meta)
